Cell Decomposition of Rank 2 Quiver Grassmannians

### 2017-04-16 Grassmannian_cells.tex
Minor edits

\begin{lemma}
  \begin{enumerate}
    \item $\tilde P_m^{(n-1)}\cong\tilde P_{m-1}^{(1)}$
    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement follows by the last section.
\end{proof}
\begin{lemma}\label{AR}
Let $m\geq 3$. Consider the short exact sequence $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$.
There exists a short exact sequence 
\[\ses{\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}}{\tilde P_m}{\tau\tilde P_{m+1}^{(k-1)}}\]
where $\tau$ denotes the Auslander-Reiten translate. Here the lifts of $P_{m-1}$ and $P_{m-2}$ have to be chosen appropriately. Moreover, we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)\cong \Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=k$, $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$ and $\tau\tilde P_{m+1}^{(k-1)}\in ~^\perp(\tilde P_{m+1}^{(k-1)})$. Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
\end{lemma}
\begin{proof}
Actually, we have $(\mathcal  S \tilde P_m)^t=\tilde P_{m+1}$ where $(\quad)^t$ is the functor induced by turning around the arrows (or taking the transpose representation). This means that it is enough to show the statement for $m=3$ as all representations appearing are not isomorphic to the simple injective representation $S_1$.

@@

We have $\Hom(\tilde P_{m+1}^{(k-1)},\tau \tilde P_{m+1}^{(k-1)})=0$ and $\Ext((\tilde P_{m+1}^{(k-1)},\tau \tilde P_{m+1}^{(k-1)})=k$. Since we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=k$ and $\Hom(\tilde P_{m+1}^{(k-1)},\tilde P_m)=0$, we have $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}\in (\tilde P_{m+1}^{(k-1)})^\perp$.

By Lemma \ref{AR}, if $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, we have $W\neq 0$. This means that $\tau\tilde P_{m+1}^{(k-1)}/W$ is a proper factor of $\tau \tilde P_{m+1}^{(k-1)}$. 
It follows that we have $\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)=0$. Indeed, by Auslander-Reiten theory every non-split morphism $g:\tau\tilde P_{m+1}^{(k-1)}\to \tau\tilde P_{m+1}^{(k-1)}/W$ factors through the middle term $Z$ of the AR-sequence 
\[\ses{\tau\tilde P_{m+1}^{(k-1)}}{Z}{\tilde P_{m+1}^{(k-1)}}\]
which means that the first map of the induced sequence
\[\Hom(\tau\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)\to\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)\to\Ext(Z,\tau\tilde P_{m+1}^{(k-1)}/W) \]
is zero. As $\tau\tilde P_{m+1}^{(k-1)}$ is exceptional (on the universal cover), we are in the situation of Ringel's reflection \cite{rin} which means that $\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=k$, $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$ and $\tau\tilde P_{m+1}^{(k-1)}\in ~^\perp(\tilde P_{m+1}^{(k-1)})$ yields $\Ext(Z,\tau\tilde P_{m+1}^{(k-1)})=0$. Thus we obtain $\Ext(Z,\tau\tilde P_{m+1}^{(k-1)}/W)=0$

@@

\begin{proposition}
  Consider $\psi:Gr^{\tilde Q}_\tbfe(\tilde P_m)\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^k \tilde P_{m-1,i})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)}$.  Then the following hold:
  \begin{enumerate}
    \item For $V\subsetneq \tilde P_m^{(k)}$ and $U\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$, we have $\psi^{-1}(U,V)=\AA^{\langle V,\bigoplus_{i=1}^k\tilde P_{m-1,i}/U\rangle}$.
    \item If $V=\tilde P_m^{(k)}$, the fibre $\psi^{-1}(U,V)$ is non-empty and of constant dimension if and only if $\Ext(\tilde P_m^{(k)},U)\neq 0$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  (1) $V$ is preprojective but $\bigoplus_{i=1}^k\tilde P_{m-1,i}/U$ is not unless $U=0$

>>>>

\begin{lemma}
  \begin{enumerate}
    \item $\tilde P_m^{(n-1)}\cong\tilde P_{m-1}^{(1)}$
    \item The subrepresentation $\bigoplus_{i=1}^{k-1}\tilde P_{m-1,i}\oplus\bigoplus_{i=1}^k\tilde P_{m-2,i}\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$ is in $(\tilde P_m^{(k)})^\perp$ and
      \[\Ext(\bigoplus_{i=1}^k\tilde P_{m-1,i},\tilde P_m^{(k)})\cong\Ext(\tilde P_{m-1}^{(k)},\tilde P_m^{(k)})\]
      where $\tilde P_{m-1}^{(k)}$ above denotes the cokernel of the inclusion.
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement follows by the last section.
\end{proof}
\begin{lemma}\label{AR}
Let $m\geq 3$. Consider the short exact sequence $\ses{\tilde P_m}{\tilde P_{m+1}^{(k)}}{\tilde P_{m+1}^{(k-1)}}$.
There exists a short exact sequence 
\[\ses{\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}}{\tilde P_m}{\tau\tilde P_{m+1}^{(k-1)}}\]
where $\tau$ denotes the Auslander-Reiten translate. Here the lifts of $P_{m-1}$ and $P_{m-2}$ have to be chosen appropriately. Moreover, we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)\cong \Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=\kk$, $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$ and $\tau\tilde P_{m+1}^{(k-1)}\in ~^\perp(\tilde P_{m+1}^{(k-1)})$. Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
\end{lemma}
\begin{proof}
Actually, we have $(\mathcal  S \tilde P_m)^t=\tilde P_{m+1}$ where $(\quad)^t$ is the functor induced by turning around the arrows (or taking the transpose representation). This means that it is enough to show the statement for $m=3$ as all representations appearing are not isomorphic to the simple injective representation $S_1$.

@@

We have $\Hom(\tilde P_{m+1}^{(k-1)},\tau \tilde P_{m+1}^{(k-1)})=0$ and $\Ext(\tilde P_{m+1}^{(k-1)},\tau \tilde P_{m+1}^{(k-1)})=\kk$. Since we have $\Ext(\tilde P_{m+1}^{(k-1)},\tilde P_m)=\kk$ and $\Hom(\tilde P_{m+1}^{(k-1)},\tilde P_m)=0$, we have $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}\in (\tilde P_{m+1}^{(k-1)})^\perp$.

By Lemma \ref{AR}, if $\Ext(\tilde P_{m+1}^{(k-1)},U)\neq 0$, we have $W\neq 0$. This means that $\tau\tilde P_{m+1}^{(k-1)}/W$ is a proper factor of $\tau \tilde P_{m+1}^{(k-1)}$. 
It follows that we have $\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)=0$. Indeed, by Auslander-Reiten theory every non-split morphism $g:\tau\tilde P_{m+1}^{(k-1)}\to \tau\tilde P_{m+1}^{(k-1)}/W$ factors through the middle term $Z$ of the AR-sequence 
\[\ses{\tau\tilde P_{m+1}^{(k-1)}}{Z}{\tilde P_{m+1}^{(k-1)}}\]
which means that the first map of the induced sequence
\[\Hom(\tau\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)\to\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)}/W)\to\Ext(Z,\tau\tilde P_{m+1}^{(k-1)}/W) \]
is zero. As $\tau\tilde P_{m+1}^{(k-1)}$ is exceptional (on the universal cover), we are in the situation of Ringel's reflection \cite{rin} which means that $\Ext(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=\kk$, $\Hom(\tilde P_{m+1}^{(k-1)},\tau\tilde P_{m+1}^{(k-1)})=0$ and $\tau\tilde P_{m+1}^{(k-1)}\in ~^\perp(\tilde P_{m+1}^{(k-1)})$ yields $\Ext(Z,\tau\tilde P_{m+1}^{(k-1)})=0$. Thus we obtain $\Ext(Z,\tau\tilde P_{m+1}^{(k-1)}/W)=0$

@@

\begin{proposition}
  Consider $\psi:Gr^{\tilde Q}_\tbfe(\tilde P_m)\to\bigsqcup_{\tbff+\tbfg=\tbfe} Gr^{\tilde Q}_\tbff(\bigoplus_{i=1}^k \tilde P_{m-1,i})\times Gr^{\tilde Q}_\tbfg(\tilde P_m^{(k)})$.  Then the following hold:
  \begin{enumerate}
    \item For $V\subsetneq \tilde P_m^{(k)}$ and $U\subset\bigoplus_{i=1}^k\tilde P_{m-1,i}$, we have $\psi^{-1}(U,V)=\AA^{\langle V,\bigoplus_{i=1}^k\tilde P_{m-1,i}/U\rangle}$.
    \item If $V=\tilde P_m^{(k)}$, the fibre $\psi^{-1}(U,V)$ is non-empty and of constant dimension if and only if $\Ext(\tilde P_m^{(k)},U)\neq 0$.
  \end{enumerate}
\end{proposition}
\begin{proof}
  (1) $V$ is preprojective but $\bigoplus_{i=1}^k\tilde P_{m-1,i}/U$ is not unless $U=0$
